### 2017-06-10 report/paper.tex
report update

\end{titlepage}
\tableofcontents
\newpage
\begin{abstract}
Common music recommender systems do not take into account the position of the customer. This piece discusses how it is possible to link a song with a POI using the semantic web.
\end{abstract}

@@

\section{Mobile Web Application}
\subsubsection{Music Player}
\subsection{Google Map API}
\subsubsection{POIs placement}
\subsubsection{Navigation}
stocazzo
\subsection{Relation visualization (and Path format)}
\section{Conclusion and Future Work}

>>>>

\end{titlepage}
\tableofcontents
\newpage
\begin{abstract}
Common music recommender systems do not take into account the position of the customer. This piece discusses how it is possible to link a song with a POI using the semantic web.

Abstract: Place is a notion closely linked with the wealth of human experience, and invested
by values, attitudes, and cultural influences. In particular, many places are strongly linked to
music, which contributes to shaping the perception and the meaning of a place. In this project we
propose a semantic based approach for finding musicians linked to a place of
interest (POI). We show a semantic-based framework built upon the DBpedia ontology, 3cixty and Doremus. Furthermore we present a graph exploration algorithm  that is able to find deep connections in a triple store in an short time and discriminate between them
graph-based algorithm that scores musicians with respect to their semantic relatedness to
a POI and suggests the top scoring ones. We found that users appreciate and judge as valuable
the musician suggestions generated by the proposed approach. Moreover, users perceived
compositions of the suggested musicians as suited for the POIs

\end{abstract}

@@

\section{Mobile Web Application}
\subsubsection{Music Player}
The music player is implemented using the Spotify Play Button. This is a special iframe that loads a simplified Spotify player for a specified playlist. This solution is extremely convenient because it simply needs a plylist ID to run. Since the playlists are created server side and are recovered using the REST API, the whole process is very simple.
Unfortunately it is not possible to manipulate programmatically the iframe and this limit the whole user experience. As an improvement, we could build a custom player that still uses the Spotify API.
\subsection{Google Map API}
\subsubsection{POIs placement}
todo: Lorenzo

\subsubsection{Navigation}

\subsection{Relation visualization (and Path format)}
todo: Lorenzo
\section{Conclusion and Future Work}
